---
title: "R Notebook"
output: html_notebook
---

```{r, include = FALSE}
library(tidyverse)
library(titanic)
```

## Import

This step could be reading a file, or loading an R package dataset into a variable.

```{r}
df <- titanic_train

df
```

## Tidy & transform

```{r}
tidy_df <- df %>%
  filter(!is.na(Age)) %>%
  mutate(is_female = ifelse(Sex == "female", 0, 1)) %>%
  select(
    -Ticket,
    -Cabin,
    -Sex,
    -PassengerId,
    -Name
  ) %>%
  rename_all(tolower)

glimpse(tidy_df)
```

## Visualization

```{r}
library(ggplot2)

ggplot(data = tidy_df) +
  geom_histogram(aes(x = age), binwidth =  5)

```


```{r}
tidy_df %>%
  mutate(age_bin = cut(age, breaks = c(0, 5, 10, 20, 30, 40, 60, 80))) %>%
  group_by(age_bin) %>%
  summarise(survived = sum(survived) / n()) %>%
  ggplot() +
  geom_col(aes(x = age_bin, y = survived))

```

## Model

```{r}
tidy_df %>%
  select(-embarked) %>%
  cor(.) 
```



```{r}
set.seed(100)

model_df <- tidy_df %>%
  select(
    -fare
  ) %>%
  sample_frac(0.8)

model1 <- glm(survived ~. , data = model_df)

summary(model1)
```

```{r}
indices <- sample(1:nrow(tidy_df), size = 0.80 * nrow(tidy_df))
train <- tidy_df[indices, ]
test  <- tidy_df[-indices, ]

model_df <- train %>%
  select(
    -fare,
    -parch,
    -sibsp,
    -embarked
  ) %>%
  mutate(age = ifelse(age <= 5, 1, 0))

model2 <- glm(survived ~. , data = model_df)

summary(model2)
```

```{r}
validation <- predict(model2, test)

val_df <- test %>%
  mutate(score = validation,
         prediction = ifelse(score < 0.7, 0, 1)) 


results <- val_df %>%
  group_by(
    survived,
    prediction
  ) %>%
  tally()

results
```



## Appendix

Data Dictionary (source: Kaggle.com)

  Variable	Definition	Key
  survival	Survival	0 = No, 1 = Yes
  pclass	Ticket class	1 = 1st, 2 = 2nd, 3 = 3rd
  sex	Sex	
  Age	Age in years	
  sibsp	# of siblings / spouses aboard the Titanic	
  parch	# of parents / children aboard the Titanic	
  ticket	Ticket number	
  fare	Passenger fare	
  cabin	Cabin number	
  embarked	Port of Embarkation	C = Cherbourg, Q = Queenstown, S = Southampton
  Variable Notes
  
  pclass: A proxy for socio-economic status (SES)
  1st = Upper
  2nd = Middle
  3rd = Lower
  
  age: Age is fractional if less than 1. If the age is estimated, is it in the form of xx.5
  
  sibsp: The dataset defines family relations in this way...
  Sibling = brother, sister, stepbrother, stepsister
  Spouse = husband, wife (mistresses and fiancés were ignored)
  
  parch: The dataset defines family relations in this way...
  Parent = mother, father
  Child = daughter, son, stepdaughter, stepson
  Some children travelled only with a nanny, therefore parch=0 for them.
